Supplementary material for "Hack Weeks as a model for Data Science Education and Collaboration"

### 2018-06-21 supplementary_material.tex
Fix typo.

\usepackage{hyperref}
\usepackage{url}
\usepackage{microtype}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{tabularx}
%\usepackage{pdflscape}
\linespread{1.2}

@@

Participants were asked to respond to statements regarding these topics using a six-point Likert-type scale. All questions were anonymously recorded. No responses were discarded, and no pre-processing was performed on the data. We test for correlations between demographic characteristics (independent variables) and question responses (dependent variables) using a standard $\chi^2$ test and compute the effect sizes via a bias-corrected version of Cram\'{e}r's V \citep{cramer1946,bergsma2013}, denoted $\phi_c$ in the manuscript. For a fairly permissive significant threshold of $\alpha < 0.05$, we require a $p$-value of $p < 0.0007$, corrected for $N_\mathrm{trials} = 36$ trials, to claim a significant effect as well as at least a small effect size according to~\citep{cohen1988}.

We note that while a non-significant $p$-value can reject a hypothesis, this is not automatically evidence for the corresponding null hypothesis, since a lack of statistical power could also originate in a too small sample size. For cases where the null hypothesis corresponds to the scientific hypothesis of interest, we perform an equivalence test based on the Cram\'{e}r's V effect size following~\citep{}. We generate 10,000 random samples via bootstrap for each response variable and compute the corresponding effect size in order to generate 90\% confidence intervals around the measured Cram\'{e}r's V. For each hypothesis, we determine an equivalence bound for Cram\'{e}r's V for a medium-strength effect size based on \citet{cohen1988} given the number of degrees of freedom and calculate the $p$-value that the measured effect size could extend above\footnote{Note that because Cram\'{e}r's V is defined on the interval $[0,1]$, we only require an upper bound} this equivalence bound. If the latter hypothesis can be rejected, this indicates that the observed effect falls within the equivalence bounds and is statistically smaller than any effect deemed worthwhile.

The full analysis procedure is available online\footnote{See the repository: \url{https://github.com/uwescience/HackWeek-Writeup}}.

@@

%\begin{landscape}
\begin{sidewaystable}

@@

\begin{tabularx}{24cm}{p{3.2cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}p{0.4cm}}

@@

\textbf{Question} & \multicolumn{9}{c}{\textbf{Astro Hack Week}} & \multicolumn{9}{c}{\textbf{GeoHackWeek}} & \multicolumn{9}{c}{\textbf{NeuroHackWeek}} \\ \midrule
 & $N$ & $\mathrm{dof}_{\chi^2}^\emph{a}$ & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}^\emph{b}$ & $\phi_c$ & $\mathrm{CI}_{\mathrm{L}}$ & $\mathrm{CI}_{\mathrm{U}}$ & $p_{\mathrm{eq}}$ 
 & $N$ & $\mathrm{dof}_{\chi^2}^\emph{a}$ & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}^\emph{b}$ & $\phi_c$ &$\mathrm{CI}_{\mathrm{L}}$ & $\mathrm{CI}_{\mathrm{U}}$ & $p_{\mathrm{eq}}$ 
 & $N$ & $\mathrm{dof}_{\chi^2}^\emph{a}$ & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}^\emph{b}$ & $\phi_c$ & $\mathrm{CI}_{\mathrm{L}}$ & $\mathrm{CI}_{\mathrm{U}}$ &$p_{\mathrm{eq}}$  \\ \midrule

@@

New topics, tools, methods (a) & 	61 & 10 &   5.64 & 0.85 & 1.93 & 0      & 0 & 0.26 & 0.12 &	36 & 6   &   2.51 & 0.87 & 1.88 & 0      & 0 & 0.31 & 0.16 &		41 & 10 & 15.53 & 0.15 & 1.90 & 0.23 & 0 & 0.32 & 0.17 \\
Improvement of research (b) & 		61 &   6 &   9.89 & 0.13 & 1.93 & 0.18 & 0 & 0.24 & 0.08 &	35 & 4   & 12.41 & 0.02 & 1.88 & 0.35 & 0 & 0.28 & 0.13 &		40 &   6 &   7.42 & 0.28 & 1.90 & 0.13 & 0 & 0.31 & 0.14 \\
Better science (c) & 				59 &   6 &   3.79 & 0.70 & 1.93 & 0      & 0 & 0.25 & 0.09 &	35 & 4   & 10.61 & 0.03 & 1.88 & 0.31 & 0 & 0.27 & 0.12 & 		40 &   4 &   5.06 & 0.29 & 1.90 & 0.11 & 0 & 0.28 & 0.12 \\
Teaching (d) & 					61 & 10 & 13.65 & 0.19 & 1.93 & 0.17 & 0 & 0.28 & 0.13 &	36 & 10 & 13.68 & 0.19 & 1.88 & 0.22 & 0 & 0.34 & 0.20 & 		40 & 10 &   6.90 & 0.74 & 1.90 &      0 & 0 & 0.33 & 0.19 \\ \midrule

@@

Improvement of research (b) & 		60 &   3 & 2.08 & 0.56 & 0.98 & 0      & 0 & 0.26 & 0.02&		35 & 2 &   5.26 & 0.07 & 0.97 & 0.30 & 0      & 0.33 & 0.07 &		40 & 3 & 7.62 & 0.05 & 0.97 & 0.34 & 0 & 0.30 & 0.05\\
Teaching (d) & 					61 &   5 & 7.30 & 0.20 & 0.98 & 0.19 & 0 & 0.30 & 0.05 & 		36 & 5 & 12.71 & 0.26 & 0.97 & 0      & 0.37 & 0.46 & 0.11 & 		40 & 5 & 3.17 & 0.67 & 0.97 & 0      & 0 & 0.36 & 0.11\\
Connection building (e) & 			61 &   4 & 3.70 & 0.45 & 0.98 & 0      & 0 & 0.28 & 0.03 & 		36 & 3 &   5.89 & 0.12 & 0.97 & 0.28 & 0      & 0.34 & 0.08 &		41 & 3 & 4.42 & 0.22 & 0.98 & 0.18 & 0 & 0.32 & 0.07 \\
Valued contributions (f) & 			57 &   4 & 5.98 & 0.20 & 0.98 & 0.18 & 0 & 0.28 & 0.03 &		34 & 5 &   9.46 & 0.09 & 0.97 & 0.36 & 0      & 0.34 & 0.08 &		38 & 5 & 6.75 & 0.34 & 0.97 & 0.21 & 0 & 0.35 & 0.10\\ \midrule

@@

Improvement of research (b)  & 	59 &   3 & 0.97   & 0.81 & 0.98 & 0      & 0 & 0.27 & 0.03 &	34 & 2 & 0.01 & 0.99 & 0.97 & 0      & 0 & 0.34 & 0.08 &			39 & 3 & 2.79 & 0.43 & 0.97 & 0      & 0 & 0.32 & 0.06 \\
Teaching (d) & 					61 &   5 & 5.63   & 0.34 & 0.98 & 0.09 & 0 & 0.31 & 0.05 &	34 & 4 & 1.29 & 0.86 & 0.97 & 0      & 0 & 0.39 & 0.12 & 			39 & 5 & 3.06 & 0.69 & 0.97 & 0      & 0 & 0.38 & 0.12 \\
Connection building (e) & 			61 &   4 & 1.64   & 0.80 & 0.98 & 0      & 0 & 0.28 & 0.04 &	34 & 3 & 8.42 & 0.04 & 0.97 & 0.40 & 0 & 0.36 & 0.09 &			40 & 3 & 3.49 & 0.32 & 0.97 & 0.10 & 0 & 0.33 & 0.07 \\
Valued contributions (f) & 			58 &   4 & 13.14 & 0.01 & 0.98 & 0.40 & 0 & 0.29 & 0.04 &	32 & 5 & 2.49 & 0.78 & 0.96 & 0      & 0 & 0.40 & 0.14 &			37 & 5 & 4.05 & 0.54 & 0.97 & 0      & 0 & 0.36 & 0.11\\

@@

\end{threeparttable}
\label{tab:survey}
%\end{table*}
\end{sidewaystable}
%\end{landscape}

@@

\section{Additional Figures}
\label{sec:suppfigures}
Here, we present a number of additional figures related to the survey data presented in the main text. The stacked bar charts presented here provide anothe view of the data that produced the results quoted in Table 1 above.

>>>>

\usepackage{hyperref}
\usepackage{url}
\usepackage{microtype}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{tabularx}
\linespread{1.2}

@@

Participants were asked to respond to statements regarding these topics using a six-point Likert-type scale. All questions were anonymously recorded. No responses were discarded, and no pre-processing was performed on the data. We tested for correlations between demographic characteristics (independent variables), questioned responses (dependent variables) using a standard $\chi^2$ test and computed the effect sizes via a bias-corrected version of Cram\'{e}r's V \citep{cramer1946,bergsma2013}, denoted $\phi_c$ in the manuscript. For a fairly permissive significant threshold of $\alpha < 0.05$, we require a $p$-value of $p < 0.0007$, corrected for $N_\mathrm{trials} = 36$ trials, to claim a significant effect as well as at least a small effect size according to~\citep{cohen1988}. The full analysis procedure is available online\footnote{See the repository: \url{https://github.com/uwescience/HackWeek-Writeup}}.

@@

\begin{table*}

@@

\begin{tabularx}{18cm}{p{3.6cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}p{0.42cm}}

@@

\textbf{Question} & \multicolumn{6}{c}{\textbf{Astro Hack Week}} & \multicolumn{6}{c}{\textbf{GeoHackWeek}} & \multicolumn{6}{c}{\textbf{NeuroHackWeek}} \\ \midrule
 & $N$ & $\mathrm{dof}_{\chi^2}^\emph{a}$ & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}^\emph{b}$ & $\phi_c$ & $N$ & $\mathrm{dof}_{\chi^2}^\emph{a}$ & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}^\emph{b}$ & $\phi_c$ & $N$ & $\mathrm{dof}_{\chi^2}^\emph{a}$ & $\chi^2$ & $p$ & $\mathrm{dof}_{\phi_c}^\emph{b}$ & $\phi_c$ \\ \midrule

@@

New topics, tools, methods (a) & 61 & 10 & 5.64 & 0.85 & 1.93 & 0 & 36 & 6 & 2.51 & 0.87 & 1.88 & 0 & 41& 10 & 15.53 & 0.15 & 1.9 & 0.23 \\
Improvement of research (b) & 61 & 6 &  9.89 & 0.13 & 1.93 & 0.18 & 35 & 4 & 12.41 & 0.02 & 1.88 & 0.35 & 40 & 6 & 7.42 & 0.28 & 1.90 & 0.13 \\
Better science (c) & 59 & 6 & 3.79 & 0.70 & 1.93 & 0 & 35 & 4 & 10.61 & 0.03 & 1.88 & 0.31 & 40 & 4 &  5.06 & 0.29 & 1.90 & 0.11\\
Teaching (d) & 61 & 10 & 13.65 & 0.19 & 1.93 & 0.17 & 36 & 10 & 13.68 & 0.19 & 1.88 & 0.22 & 40 & 10 & 6.90 & 0.74 & 1.90 & 0 \\ \midrule

@@

Improvement of research (b) & 60 & 3 & 2.08 & 0.56 & 0.98 & 0 & 35 & 2 & 5.26 & 0.07 & 0.97 & 0.30 & 40 & 3 & 7.62 & 0.05 & 0.97 & 0.34\\
Teaching (d) & 61 & 5 & 7.30 & 0.20 & 0.98 & 0.19 & 36 & 5 & 12.71 & 0.26 & 0.97 & 0.46 & 40 &5 & 3.17 & 0.67 & 0.97 & 0 \\
Connection building (e) & 61 & 4 & 3.70 & 0.45 & 0.98 & 0 & 36 & 3 & 5.89 & 0.12 & 0.97 & 0.28 & 41 & 3 & 4.42 & 0.22 & 0.98 & 0.18\\
Valued contributions (f) & 57 & 4 & 5.98 & 0.20 & 0.98 & 0.18 & 34 & 5 & 9.46 & 0.09 & 0.97 & 0.36 & 38 & 5 & 6.75 & 0.34 & 0.97 & 0.21 \\ \midrule

@@

Improvement of research (b)  & 59 & 3 & 0.97 & 0.81 & 0.98 & 0 & 34 &2 & 0.01 & 0.99 & 0.97 & 0 & 39 & 3 & 2.79 & 0.43 & 0.97 & 0 \\
Teaching (d) & 61 & 5 & 5.63 & 0.34 & 0.98 & 0.09 & 34 & 4 & 1.29 & 0.86 & 0.97 & 0 & 39 & 5 & 3.06 & 0.69 & 0.97 & 0 \\
Connection building (e) & 61 & 4 & 1.64 & 0.80 & 0.98 & 0 & 34 & 3 & 8.42 & 0.04 & 0.97 & 0.40 & 40 & 3 & 3.49 & 0.32 & 0.97 & 0.10 \\
Valued contributions (f) & 58 & 4 & 13.14 & 0.01 & 0.98 & 0.40 & 32 & 5 & 2.49 & 0.78 & 0.96 & 0 & 37 & 5 & 4.05 & 0.54 & 0.97 & 0 \\

@@

\end{threeparttable}
\label{tab:survey}
%\end{table*}
\end{table*}

@@

\section{Additional Figures}
\label{sec:suppfigures}
Here, we present a number of additional figures related to the survey data presented in the main text. The stacked bar charts presented here provide another view of the data that produced the results quoted in Table 1 above.
